### 2014-10-09 writing/AAAI SSS '15/wordnet.tex
Add draft of WordNet section

% TODO: Fill out

@@

We extract three types of relation from WordNet. \ii{Hypernym} and \ii{hyponym} can be are represented
directly in the WordNet graph structure, and correspond closely to the \natrev and \natfor relations from
natural logic. As in natural logic, these relations are mirror images of one another: if \ii{dog} is a
hyponym of \ii{animal}, then \ii{animal} must be a hypernym of \ii{dog}.

% Wordnet! Subsumption lattice for words!

% Three relations: Hyper, hypo, coordinate
% Explain extraction and rationale for each

% Data creation:
% - Enumerate filtering strategy

% Experiment:
% - Explain train test split

% Reults:
% RNN / RNTN x Data volume x Accuracy vs. MacroF1

>>>>

@@

We extract three types of relation from WordNet. \ii{Hypernym} and \ii{hyponym} can be are represented
directly in the WordNet graph structure, and correspond closely to the $\natrev$ and $\natfor$ relations from
natural logic. As in natural logic, these relations are mirror images of one another: if \ii{dog} is a
hyponym of \ii{animal} (perhaps indirectly by way of \ii{canid}, \ii{mammal}, etc.), then \ii{animal} must be a 
hypernym of \ii{dog}. A third informative relation can 
be readily derived from the graph, which we call \ii{coordinate}. Coordinate terms are those which share
a direct hypernym, like \ii{dalmation}, \ii{pug}, and \ii{puppy}, which are all direct hyponyms of \ii{dog}. 
Coordinate terms tend to exclude one another (as with $\natalt$ above) \cite{Hurford:1974}, but this tendancy
is not universal. WordNet defines hypernymy and hyponymy over sets of synonyms, rather than over individual 
terms, so we do not include a \ii{synonym} or \ii{equivalent} relation, but rather simply consider only one
member of each set of synonyms.

To limit the size of the vocabulary without otherwise simplifying the learning problem, we extract all of the
instances of these three relations for those terms in WordNet that are hyponyms of the node \texttt{organism.n.01}.
In order to balance the distribution of the classes, we slightly downsample instances of the \ii{coordinate} relation,
yielding 36,772 relations among 3,217 terms. We randomly select 15\% of these relations as test data, and train on
some or all of the remaining data.

We find that with only a small amount of hyperparamater tuning, our model can perform almost perfectly, and that performance remains fairly good even when the fraction of the training data used is decreased.

% TODO: Describe use of GloVe once there are clearer results. Should we omit mention of it entirely?

\begin{table}[h]
\centering\resizebox{4in}{!}{\small
  \setlength{\tabcolsep}{15pt}
  \renewcommand{\arraystretch}{1.1}
  \begin{tabular}{l c l l} 
    \toprule
    Comparison layer & \% training data & w/ GloVe & w/o GloVe \\
    NN       & 100\%   & TODO & TODO \\
    NN       & 75\%   & 98.6 (100.0) & TODO \\
    NN       & 33\%   & TODO & 37.0 (37.0) \\ % TODO: See if this improves
    NN       & 16\%   & TODO & 92.0 (100.0)\\
    NTN       & 100\%   & 99.6 (100.0) & 99.4 (99.9) \\
    NTN       & 75\%   & 98.6 (100.0) & TODO\\
    NTN       & 33\%   & 95.1 (99.8) & 95.2 (100.0) \\
    NTN       & 16\%   & 94.6 (100.0) & 92.1 (100.0) \\
    \bottomrule
  \end{tabular}}
 \caption{Test (train) accuracy figures on the WordNet data.\label{b-table}}  
\end{table}
